l

### 2020-03-10 random/career_preparation/resume/resume2.tex
updates

%-------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
\section{SKILLS}
\textbf{Languages:} Python, Julia, Go, Bash, C/C++, SQL\\
\textbf{Packages:} PyTorch, Gym, TensorFlow, Scikit-Learn, Pandas, Flask \\
\textbf{Spoken:} Fluent English. Classroom Hindi, Spanish, and Mandarin

%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------
\section{EXPERIENCE}
\textbf{Fermilab - LSST Machine Learning Intern\hfill Jun - Aug 2019}\\
\textbullet{Researched applications of neural differential equations in astronomy for the Large Synoptic Survey Telescope (LSST)\\}
\textbullet{Used PLAsTiCC Astronomical Kaggle dataset to train a neural network to approximate the differential equation of different objects' light curves (brightness over time)}\\
\textbullet{Presented poster of my work on Neural-ODEs at 2019 LSST Conference in Arizona}\\
\textbullet{Worked with peers and mentors to create a high level API for fast prototyping and ensemble training of neural networks for astronomy datasets, primarily in PyTorch}
\begin{itemize}
    \item \textbf{Tools:} TorchDiffEq, DifferentialEquations.jl, PyTorch, TensorFlow, Matplotlib, Astropy, Python, Julia
    \item \textbf{Link :} github.com/deepskies/cosmoNODE and /dsutils

\end{itemize}

@@

\textbf{gym-sips: reinforcement learning in sports betting on google cloud}\hfill\\ 
\textbullet{Concurrent scraping live odds and scores $\sim$500 games/day on Linux virtual machines}\\
\textbullet{Created discrete and continuous action space gym environment for asset allocation}\\
\textbullet{Tested the PPO, SAC, and DDPG algorithms from OpenAI's Spinning Up in RL}\\
\textbullet{Agent learns to hedge across time and returns a positive net reward on test set}

\begin{itemize}
\item \textbf{Tools:} pytorch, gym, spinningup, go
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/anandijain/sips /sipgo /gym-sips 
\end{itemize}
\textbf{sippyart: variational-autoencoders for music generation}\\ 
\textbullet{Built tool to recreate images and 1-2 second sections of audio using convolutional variational autoencoders running on GPU}\\
\textbullet{Model learns to recreate melody better than rhythm, examples in README}\\
\begin{itemize}
\item \textbf{Tools:} pytorch, torchaudio, torchvision
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/anandijain/sippyart
\end{itemize}
\textbf{codebyhand: applying handwriting recognition}\\ 
\textbullet{Wrote `paint` program that infers EMNIST characters after each stroke and allows transfer learning on own handwriting}\\
\textbullet{Saves new labeled data to disk in Pytorch ImageFolder format for retraining}\\
\begin{itemize}
\item \textbf{Tools:} pytorch, torchvision, tkinter 
\end{itemize}
\begin{itemize}
\item \textbf{Link :} github.com/anandijain/codebyhand
\end{itemize}
\section{ACTIVITIES}
\textbf{UCQuantum (.org) - Founder/President}\hfill \textbf{Aug 2019 - Now}\\
\textbullet{Undergraduate Student Organization of $\sim$50 facebook group members, $\sim$10 active}\\
\textbullet{Toured Prof. David Schuster's lab and learned about cooling to superconducing temperatures and software interfaces to quantum computers}\\
\textbullet{Planning a hackathon in spring to make Prof. Schuster's computers compatible with QuTiP and qiskit}
%-------------------------------------------------------------------------------
\end{resume}
\(\)\end{document}

>>>>

%-------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
\section{SKILLS}
\textbf{Languages:} Python, Go, Julia, Bash, C/C++, SQL\\
\textbf{Packages:} PyTorch, Gym, TensorFlow, Scikit-Learn, Pandas, Flask \\
\textbf{Spoken:} Fluent English. Classroom Hindi, Spanish, and Mandarin

%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------
\section{EXPERIENCE}
\textbf{Fermilab - LSST Machine Learning Intern\hfill Jun - Aug 2019}\\
\textbullet{Researched applications of neural differential equations in astronomy for the Large Synoptic Survey Telescope (LSST)\\}
\textbullet{Used PLAsTiCC Astronomical Kaggle dataset to train a neural network to approximate the differential equation of different objects' light curves (brightness over time)}\\
\textbullet{Presented poster of my work on Neural-ODEs at 2019 LSST Conference in Arizona}\\
\textbullet{Worked with peers and mentors to create a high level API for Auto-ML and visualization of astronomy datasets, primarily in PyTorch and Matplotlib}\\
\textbf{tools:} DifferentialEquations.jl, PyTorch, TensorFlow, Matplotlib, Python, Julia\\
\textbf{src :} deepskies/cosmoNODE and deepskies/dsutils

@@

\textbf{gym-sips: reinforcement learning in sports betting on google cloud}\hfill\\ 
\textbullet{Concurrent scraping $\sim$1000 games/day of odds, scores on Linux VM to Cloud SQL}\\
\textbullet{Created discrete and continuous action space gym environment for asset allocation}\\
\textbullet{Tested the PPO, SAC, and DDPG algorithms from OpenAI's Spinning Up in RL}\\
\textbullet{Agent learns to hedge across time and returns a positive net reward on test set}\\
\textbf{tools:} pytorch, gym, spinningup, go\\
\textbf{src :} github.com/anandijain/sips /sipgo and /gym-sips

\textbf{sippyart: variational-autoencoders for music generation}\\ 
\textbullet{Built tool to recreate images and 1-2 second sections of audio using convolutional variational autoencoders running on GPU}\\
\textbullet{Model learns to recreate melody better than rhythm, examples in README}\\
\textbf{tools:} pytorch, torchaudio, torchvision, opencv\\
\textbf{src :} github.com/anandijain/sippyart

\textbf{codebyhand: applying handwriting recognition}\\ 
\textbullet{Wrote `paint` program that infers EMNIST characters after each stroke and allows transfer learning on own handwriting}\\
\textbullet{Saves new labeled data to disk in Pytorch ImageFolder format for retraining}\\
\textbf{tools:} pytorch, torchvision, tkinter \\
\textbf{src :} github.com/anandijain/codebyhand\\

\section{ACTIVITIES}
\textbf{UCQuantum (.org) - Founder/President}\hfill \textbf{Aug 2019 - Now}\\
\textbullet{Undergraduate Student Organization of $\sim$50 facebook group members, $\sim$10 active}\\
\textbullet{Toured Prof. David Schuster's lab and learned about cooling to superconducing temperatures and software interfaces to quantum computers}\\
\textbullet{Planning a hackathon in spring to make Prof. Schuster's computers compatible with QuTiP and qiskit}
%-------------------------------------------------------------------------------
\end{resume}
\(\)\end{document}
